---
title: "Spatial Extension"
author: "Tim Ravis"
date: "4/21/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
require(tidyverse)
require(sf)
require(spdep)
require(coefplot)
require(leaflet)
require(rlist)
require(huxtable)
```

```{r load data, include = FALSE}
# load data—raw, pre-matching, matched (from paper)

raw_data <- read_csv("TitlingDeforestation/BHM_sample20.csv")
data.PMLonly.flat <- read_csv("TitlingDeforestation/PML_prematching.csv")
data.PMLonly.flat.matched <- read_csv("TitlingDeforestation/PMLonly_flat_matched_140414.csv")
data.PMI.flat <- read_csv("TitlingDeforestation/PMI_prematching.csv")
data.PMI.flat.matched <- read_csv("TitlingDeforestation/PMI_flat_matched_140414.csv")

```
#### Introducing Spatial Autocorrelation

*Everything is related to everything else, but near things are more related than distant things.* Tobler's First Law of Geography [-@Tobler]

Show it visually in the data on treatment, outcome, and pre-treatment
Global measure--Moran
- discuss weights, note that using a distance neighborhood rather than a knn

#### Intro LISA 
getis ord
Show it on at least pre-treatment (outcome? (interaction of two?) treatment?)

*Show how it affects the models with the data provided by the paper

*Explain may be misleading bc panel spatial data, rematch only for year one
Show distribution of years in matched datasets too
How are models affected?



Can I rematch for only year one and total loss over five years?
Can i drop correlated vars from the models when replacing w g?
Can i do a 



```{r import & viz as spatial data, echo = FALSE}

# convert the matched csv to sf using sf package

spatial_PMI_matched <- st_as_sf(data.PMI.flat.matched, 
                        coords = c("long", "lat"), crs = 4326) 

spatial_PMI_prematch<- st_as_sf(data.PMI.flat, 
                        coords = c("LONG", "LAT"), crs = 4326) 
                        
spatial_PML_matched <- st_as_sf(data.PMLonly.flat.matched, 
                        coords = c("long", "lat"), crs = 4326) 

spatial_PML_prematch <- st_as_sf(data.PMLonly.flat, 
                        coords = c("LONG", "LAT"), crs = 4326)

# visualizing spatial autocorrelation of outcome pre-treatment each matched set

plot(spatial_PML_matched["fl.pre.5cell"], axes = TRUE, pch = 20, cex = 0.1, breaks = "kmeans")
plot(spatial_PML_matched["fl.5yr.postPML"], axes = TRUE, pch = 20, cex = 0.1, breaks = "kmeans")
plot(spatial_PML_matched["PML"], axes = TRUE, pch = 20, cex = 0.1)

plot(spatial_PMI_matched["fl.pre.5cell"], axes = TRUE, pch = 20, cex = 0.1, breaks = "kmeans")
plot(spatial_PMI_matched["fl.5yr.postPML"], axes = TRUE, pch = 20, cex = 0.1, breaks = "kmeans")
plot(spatial_PMI_matched["PMI"], axes = TRUE, pch = 20, cex = 0.1)

```

```{r leaflet, include = TRUE}
#pal <- colorBin("magma", domain = spatial_PML_matched$fl.pre.5cell, bins = 10)
pal <- colorBin("magma", domain = spatial_PML_matched$nbsize, bins = 10)
#pal <- colorQuantile("magma", domain = spatial_PML_matched$fl.pre.5cell)
leaflet(st_transform(spatial_PML_matched, 4326)) %>%
  setView(-77.93, -2.82, 8) %>%
  addProviderTiles("Stamen.Toner") %>%
  addCircleMarkers(fillColor = ~pal(nbsize), 
                   stroke = FALSE,
                   radius = 3,
                   fillOpacity = 1) %>%
  addLegend(
    pal = pal, 
    values = ~nbsize, 
    opacity = 1,
    title = NULL,
    position = "bottomright")
```

```{r echo = FALSE}

# create neighborhood--list of vectors, each containing the set of points 
# that fall within certain radius of a given point

d_PML_matched <- dnearneigh(spatial_PML_matched, 0, 10)
d_PMI_matched <- dnearneigh(spatial_PMI_matched, 0, 10)

d_PML_prematch <- dnearneigh(spatial_PML_prematch, 0, 10)
d_PMI_prematch <- dnearneigh(spatial_PMI_prematch, 0, 10)

# distance has edge effects...control for number in neighborhood?
# drop observations with a neighborhood that's only overlapping obs
# first attach to the spatial datasets, select only rows w nb > 4)

spatial_PML_matched <- spatial_PML_matched %>% 
  mutate(nbsize = sapply(d_PML_matched, length)) %>% 
  filter(nbsize > 4)
spatial_PMI_matched <- spatial_PMI_matched %>% 
  mutate(nbsize = sapply(d_PMI_matched, length)) %>% 
  filter(nbsize > 4)

spatial_PML_prematch <- spatial_PML_prematch %>% 
  mutate(nbsize = sapply(d_PML_prematch, length)) %>% 
  filter(nbsize > 4)
spatial_PMI_prematch <- spatial_PMI_prematch %>% 
  mutate(nbsize = sapply(d_PMI_prematch, length)) %>% 
  filter(nbsize > 4)

# then drop zero lengths fron the nb object

d_PML_matched <- subset.nb(d_PML_matched, sapply(d_PML_matched, length) > 4)
d_PMI_matched <- subset.nb(d_PMI_matched, sapply(d_PMI_matched, length) > 4)

d_PML_prematch <- subset.nb(d_PML_prematch, sapply(d_PML_prematch, length) > 4)
d_PMI_prematch <- subset.nb(d_PMI_prematch, sapply(d_PMI_prematch, length) > 4)

# Convert neighborhood to weight list.

w_list_PML_matched_d <- nb2listw(neighbours = d_PML_matched, style = 'W')
w_list_PMI_matched_d <- nb2listw(neighbours = d_PMI_matched, style = 'W')

w_list_PML_prematch_d <- nb2listw(neighbours = d_PML_prematch, style = 'W')
w_list_PMI_prematch_d <- nb2listw(neighbours = d_PMI_prematch, style = 'W')

```

```{r moran's i stuff, include = FALSE}

# calculate moran's I for each variable

PML_global_moran_pre <- moran.test(x = spatial_PML_matched$fl.pre.5cell,
                           listw = w_list_PML_matched_d)
PML_global_moran_treat <- moran.test(x = spatial_PML_matched$PML,
                           listw = w_list_PML_matched_d)
PML_global_moran_outcome <- moran.test(x = spatial_PML_matched$fl.5yr.postPML,
                           listw = w_list_PML_matched_d)

PMI_global_moran_pre <- moran.test(x = spatial_PMI_matched$fl.pre.5cell, 
                           listw = w_list_PMI_matched_d)
PMI_global_moran_treat <- moran.test(x = spatial_PMI_matched$PMI,
                           listw = w_list_PMI_matched_d)
PMI_global_moran_outcome <- moran.test(x = spatial_PMI_matched$fl.5yr.postPML,
                           listw = w_list_PMI_matched_d)

# moran plots PML

moran.plot(spatial_PML_matched$fl.pre.5cell, w_list_PML_matched_d)
moran.plot(spatial_PML_matched$PML, w_list_PML_matched_d)
moran.plot(spatial_PML_matched$fl.5yr.postPML, w_list_PML_matched_d)

# moran plots PMI

moran.plot(spatial_PMI_matched$fl.pre.5cell, w_list_PMI_matched_d)
moran.plot(spatial_PMI_matched$PMI, w_list_PMI_matched_d)
moran.plot(spatial_PMI_matched$fl.5yr.postPML, w_list_PMI_matched_d)

# moran mc PML

PML_mc_pre <- moran.mc(spatial_PML_matched$fl.pre.5cell, w_list_PML_matched_d, nsim = 4000)
hist(PML_mc_pre$res)
abline(v = PML_global_moran_pre[['estimate']]['Moran I statistic'], col = 'red', lwd = 2)

PML_mc_treat <- moran.mc(spatial_PML_matched$PML, w_list_PML_matched_d, nsim = 4000)
hist(PML_mc_treat$res)
abline(v = PML_global_moran_treat[['estimate']]['Moran I statistic'], col = 'red', lwd = 2)

PML_mc_outcome <- moran.mc(spatial_PML_matched$fl.5yr.postPML, w_list_PML_matched_d, nsim = 4000)
hist(PML_mc_outcome$res)
abline(v = PML_global_moran_outcome[['estimate']]['Moran I statistic'], col = 'red', lwd = 2)

# moran mc PMI

PMI_mc_pre <- moran.mc(spatial_PMI_matched$fl.pre.5cell, w_list_PMI_matched_d, nsim = 4000)
hist(PMI_mc_pre$res)
abline(v = PMI_global_moran_pre[['estimate']]['Moran I statistic'], col = 'red', lwd = 2)

PMI_mc_treat <- moran.mc(spatial_PMI_matched$PMI, w_list_PMI_matched_d, nsim = 4000)
hist(PMI_mc_treat$res)
abline(v = PMI_global_moran_treat[['estimate']]['Moran I statistic'], col = 'red', lwd = 2)

PMI_mc_outcome <- moran.mc(spatial_PMI_matched$fl.5yr.postPML, w_list_PMI_matched_d, nsim = 4000)
hist(PMI_mc_outcome$res)
abline(v = PMI_global_moran_outcome[['estimate']]['Moran I statistic'], col = 'red', lwd = 2)
```

```{r applying LISA w distance weights, fig.cap= "Local Getis-Ord values", echo = FALSE}


## matched PML getis ord

# pre treatment
g_PML_matched_pre_d <- localG(as.numeric(spatial_PML_matched$fl.pre.5cell), 
                listw = w_list_PML_matched_d,
                zero.policy = FALSE,
                return_internals = TRUE)
# treatment
g_PML_matched_treat_d <- localG(as.numeric(spatial_PML_matched$PML), 
                listw = w_list_PML_matched_d,
                zero.policy = FALSE,
                return_internals = TRUE)
# outcome
g_PML_matched_outcome_d <- localG(as.numeric(spatial_PML_matched$fl.5yr.postPML), 
                listw = w_list_PML_matched_d,
                zero.policy = FALSE,
                return_internals = TRUE)

## matched PMI getis ord

# pre treatment
g_PMI_matched_pre_d <- localG(as.numeric(spatial_PMI_matched$fl.pre.5cell), 
                listw = w_list_PMI_matched_d,
                zero.policy = FALSE,
                return_internals = TRUE)


## prematched PML getis ord

# pre treatment
g_PML_prematch_pre_d <- localG(as.numeric(spatial_PML_prematch$fl.pre.5cell), 
                listw = w_list_PML_prematch_d,
                zero.policy = FALSE,
                return_internals = TRUE)


## prematched PMI getis ord

# pre treatment
g_PMI_prematch_pre_d <- localG(as.numeric(spatial_PMI_prematch$fl.pre.5cell), 
                listw = w_list_PMI_prematch_d,
                zero.policy = FALSE,
                return_internals = TRUE)

```

```{r visualizing the g values, echo = FALSE}

# attaching matched g values to PML dataset

spatial_PML_matched$gpre <- attr(g_PML_matched_pre_d, 'internals')[,1]
spatial_PML_matched$gtreat <- attr(g_PML_matched_treat_d, 'internals')[,1]
spatial_PML_matched$goutcome <- attr(g_PML_matched_outcome_d, 'internals')[,1]

# attaching matched g values to PMI dataset

spatial_PMI_matched$gpre <- attr(g_PMI_matched_pre_d, 'internals')[,1]

# attaching prematched g values to PML dataset

spatial_PML_prematch$gpre <- attr(g_PML_prematch_pre_d, 'internals')[,1]

# attaching prematched g values to PMI dataset

spatial_PMI_prematch$gpre <- attr(g_PMI_prematch_pre_d, 'internals')[,1]

plot(spatial_PML_matched['nbsize'], axes = TRUE, pch = 20, cex = 0.1, breaks = "jenks")
plot(spatial_PML_matched['gpre'], axes = TRUE, pch = 20, cex = 0.1, breaks = "jenks")
plot(spatial_PML_matched['gtreat'], axes = TRUE, pch = 20, cex = 0.1, breaks = "jenks")
plot(spatial_PML_matched['goutcome'], axes = TRUE, pch = 20, cex = 0.1, breaks = "jenks")
```


```{r storing knn weight stuff, include = FALSE}

# create adjacency matrices; first, a matrix with the indices of points
# belonging to the set of the k nearest neighbors of each other. 

knn_PML_matched <- knearneigh(spatial_PML_matched, k = 6, longlat = TRUE)
knn_PML_prematch <- knearneigh(spatial_PML_prematch, k = 6, longlat = TRUE)
knn_PMI_matched <- knearneigh(spatial_PMI_matched, k = 6, longlat = TRUE)
knn_PMI_prematch <- knearneigh(spatial_PMI_prematch, k = 6, longlat = TRUE)

# making neighborhoods

neighborhood_PML_matched <- knn2nb(knn_PML_matched)
neighborhood_PML_prematch <- knn2nb(knn_PML_prematch)
neighborhood_PMI_matched <- knn2nb(knn_PMI_matched)
neighborhood_PMI_prematch <- knn2nb(knn_PMI_prematch)

# Convert to adjacency weight list.

w_list_PML_matched <- nb2listw(neighbours = neighborhood_PML_matched, style = 'W')
w_list_PML_prematch <- nb2listw(neighbours = neighborhood_PML_prematch, style = 'W')
w_list_PMI_matched<- nb2listw(neighbours = neighborhood_PMI_matched, style = 'W')
w_list_PMI_prematch <- nb2listw(neighbours = neighborhood_PMI_prematch, style = 'W')

g_PML_matched <- localG(as.numeric(spatial_PML_matched$fl.pre.5cell), 
                listw = w_list_PML_matched,
                zero.policy = FALSE,
                return_internals = TRUE)
g_PML_prematch <- localG(as.numeric(spatial_PML_prematch$fl.pre.5cell), 
                listw = w_list_PML_prematch,
                zero.policy = FALSE,
                return_internals = TRUE)
g_PMI_matched <- localG(as.numeric(spatial_PMI_matched$fl.pre.5cell), 
                listw = w_list_PMI_matched,
                zero.policy = FALSE,
                return_internals = TRUE)
g_PMI_prematch <- localG(as.numeric(spatial_PMI_prematch$fl.pre.5cell), 
                listw = w_list_PMI_prematch,
                zero.policy = FALSE,
                return_internals = TRUE)


spatial_PML_matched$g <- attr(g_PML_matched, 'internals')[,1]
spatial_PML_prematch$g <- attr(g_PML_prematch, 'internals')[,1]
spatial_PMI_matched$g <- attr(g_PMI_matched, 'internals')[,1]
spatial_PMI_prematch$g <- attr(g_PMI_prematch, 'internals')[,1]

plot(spatial_PML_matched['g'], axes = TRUE, pch = 20, cex = 0.1, breaks = "jenks")

```


```{r retrying fig 4 (PML only), echo = FALSE}

# matched models

fig4.a.lisa.PML.pre <- lm(fl.5yr.postPML ~ PML + fl.pre.5cell + forest.pre +
               pop.den.5km.pre + dist.disturb.pre + A128 + A129 +
               A130 + A154 + A347 + A361 + A362 + gpre + nbsize, data = spatial_PML_prematch)

fig4.b.lisa.PML.pre <- lm(fl.5yr.postPML ~ PML, weights = weights,
             data = spatial_PML_matched)

fig4.c.lisa.PML.pre <- lm(fl.5yr.postPML ~ PML + fl.pre.5cell + forest.pre +
             pop.den.5km.pre + dist.disturb.pre +
             A128 + A129 + A130 + A154 + A347 + A361 + A362 + gpre + nbsize,
             weights = weights, data = spatial_PML_matched)

```
```{r make original figure 4, echo = FALSE}

# generating the coefplot from the paper for PML data

fig4.lisa.PML.pre <- multiplot(fig4.a.lisa.PML.pre, 
                               fig4.b.lisa.PML.pre, 
                               fig4.c.lisa.PML.pre, 
                               coefficients = "PML",
                  names = c("(a)", "(b)", "(c)"), title = NULL,
                  ylab = NULL, xlab = expression(paste(
                    "Effect on deforestation over 5 years (",
                    m^{2} , " per " , km^{2}, ")")), pointSize = 3,
                  lwdOuter = 0.5, lwdInner = 1.5, horizontal = TRUE,
                  secret.weapon = TRUE, color = "black")

fig4.lisa.PML.pre + theme_minimal()
```

```{r retrying fig 6 (PMI), echo = FALSE}

# matched models

fig4.a.lisa.PMI.pre <- lm(fl.5yr.postPML ~ PMI + fl.pre.5cell + forest.pre +
               pop.den.5km.pre + dist.disturb.pre + A128 + A129 +
               A130 + A154 + A347 + A361 + A362 + gpre + nbsize, 
               data = spatial_PMI_prematch)

fig4.b.lisa.PMI.pre <- lm(fl.5yr.postPML ~ PMI, weights = weights,
             data = spatial_PMI_matched)

fig4.c.lisa.PMI.pre <- lm(fl.5yr.postPML ~ PMI + fl.pre.5cell + forest.pre +
             pop.den.5km.pre + dist.disturb.pre +
             A128 + A129 + A130 + A154 + A347 + A361 + A362 + gpre + nbsize,
             weights = weights, data = spatial_PMI_matched)

```
```{r make original figure 4, echo = FALSE}

# generating the coefplot from the paper for PML data

fig4.lisa.PMI.pre <- multiplot(fig4.a.lisa.PMI.pre, 
                               fig4.b.lisa.PMI.pre, 
                               fig4.c.lisa.PMI.pre, 
                               coefficients = "PMI",
                  names = c("(a)", "(b)", "(c)"), title = NULL,
                  ylab = NULL, xlab = expression(paste(
                    "Effect on deforestation over 5 years (",
                    m^{2} , " per " , km^{2}, ")")), pointSize = 3,
                  lwdOuter = 0.5, lwdInner = 1.5, horizontal = TRUE,
                  secret.weapon = TRUE, color = "black")

fig4.lisa.PMI.pre + theme_minimal()
```

```{r table for PML models, echo = FALSE}
# make huxtable object

table3 <- huxreg("Model A" = fig4.a.lisa.PML.pre, 
                 "Model B" = fig4.b.lisa.PML.pre, 
                 "Model C" = fig4.c.lisa.PML.pre,
                 coefs = c("(Intercept)" = "(Intercept)",
                           "PML (treatment)" = "PML",
                           "Pre-treatment Forest Loss" = "fl.pre.5cell",
                           "Pre-treatment Forest Cover" = "forest.pre",
                           "Population Density" = "pop.den.5km.pre",
                           "Distance to Disturbed Land Classification" = "dist.disturb.pre",
                           "Distance to Electric Grid" = "A128",
                           "Distance to Major River" = "A129",
                           "Distance to Major Roads" = "A130",
                           "Shaur Indigenous Land" = "A154",
                           "Protected Area Status" = "A347",
                           "Elevation" = "A361",
                           "Slope" = "A362",
                           "Getis-Ord G" = "gpre",
                           "Neighborhood Size" = "nbsize"),
                 statistics = c('Total Observations' = 'nobs',
                                'R squared' = 'r.squared'),
                 number_format = 2) %>%
  set_caption("Table 3: Extended Results, PML-only treatment (2002)")

table3
```

```{r table for PMI models, echo = FALSE}
# make huxtable object

table4 <- huxreg("Model A" = fig4.a.lisa.PMI.pre, 
                 "Model B" = fig4.b.lisa.PMI.pre, 
                 "Model C" = fig4.c.lisa.PMI.pre,
                 coefs = c("(Intercept)" = "(Intercept)",
                           "PMI (treatment)" = "PMI",
                           "Pre-treatment Forest Loss" = "fl.pre.5cell",
                           "Pre-treatment Forest Cover" = "forest.pre",
                           "Population Density" = "pop.den.5km.pre",
                           "Distance to Disturbed Land Classification" = "dist.disturb.pre",
                           "Distance to Electric Grid" = "A128",
                           "Distance to Major River" = "A129",
                           "Distance to Major Roads" = "A130",
                           "Shaur Indigenous Land" = "A154",
                           "Protected Area Status" = "A347",
                           "Elevation" = "A361",
                           "Slope" = "A362",
                           "Getis-Ord G" = "gpre",
                           "Neighborhood Size" = "nbsize"),
                 statistics = c('Total Observations' = 'nobs',
                                'R squared' = 'r.squared'),
                 number_format = 2) %>%
  set_caption("Table 4: Extended Results, PMI + PML treatment (2003-2007)")

table4
```

```{r rematching genetically, include = FALSE}

# authors wrote this to prep data for matching

make <- function (data, names) {
  datasub <- as.data.frame(data)
  sub = substitute(names)
  names <- as.character(sub)
  data.make <- subset(datasub,select = names(datasub) %in% names)
  data.make <<- na.omit(data.make)
  data.make <- na.omit(data.make)
  print(c("ob =",nrow(data.make)),quote=F)
}

# PML only matching

make(spatial_PML_prematch, c(fl.5yr.postPML, fl.yr1, fl.yr2, fl.yr3, fl.yr4,
   fl.yr5, PML, fl.pre.5cell, forest.pre,
   pop.den.5km.pre, dist.disturb.pre, A128, A129,
   A130, A154, A347, A361, A362, id, LAT, LONG, gpre, nbsize))

out.PMLonly.flat <- matchit(PML ~ fl.pre.5cell + forest.pre +
  pop.den.5km.pre + dist.disturb.pre +
  A128 + A129 + A130 + A154 + A347 +
  A361 + A362 + gpre + nbsize, method = "genetic",
  int.seed = 104, unif.seed = 104,
  pop.size = 1500, wait.generations = 20,
  MemoryMatrix = FALSE, ties = FALSE,
  discard = "control", data = data.make)

data.PMLonly.flat.matched <- match.data(out.PMLonly.flat)

# PMI matching

make(spatial_PMI_prematch, c(fl.5yr.postPML, fl.yr1, fl.yr2, fl.yr3, fl.yr4,
                      fl.yr5, PMI, fl.pre.5cell, forest.pre, pop.den.5km.pre,
                      dist.disturb.pre, A128, A129, A130, A154, A347, A361,
                      A362, id, LAT, LONG, gpre, nbsize))

out.PMI.flat <- matchit(PMI ~ fl.pre.5cell + forest.pre + pop.den.5km.pre +
                        dist.disturb.pre + A128 + A129 + A130 + A154 + A347 +
                        A361 + A362 + gpre + nbsize, method = "genetic", int.seed = 101,
                        unif.seed = 101, pop.size = 500, wait.generations = 20,
                        MemoryMatrix = FALSE, ties = FALSE,
                        discard = "control", data=data.make)

data.PMI.flat.matched <- match.data(out.PMI.flat)


# NOTE SELF: need to figure out how best to get the spatial data into these—
# they use variables that are not included in the "_select" csvs...
```









```{r looking for vars to drop, echo = FALSE, warning = FALSE}

# create a pairs plot w the model variables matched and prematched

corrz <- data.PMLonly.flat.matched %>% 
  select(PML, fl.pre.5cell, forest.pre, pop.den.5km.pre,
         dist.disturb.pre, A128, A129, A130, A154, 
         A347, A361, A362) %>% 
  mutate(PML = as.factor(PML)) %>% 
  mutate(gd = spatial_PML_matched$gd) %>% 
  mutate(nbsize = spatial_PML_matched$nbsize)

# PML + fl.pre.5cell + forest.pre +
#                pop.den.5km.pre + dist.disturb.pre + A128 + A129 +
#                A130 + A154 + A347 + A361 + A362 

my_cols <- c("#FC4E07", "#00AFBB")

panel.cor <- function(x, y){
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    r <- round(cor(x, y), digits=2)
    txt <- paste0("R = ", r)
    cex.cor <- 0.8/strwidth(txt)
    text(0.5, 0.5, txt, cex = cex.cor * r)
}   

upper.panel <- function(x, y){
  points(x, y, pch = 20, cex = 0.2, col = my_cols[corrz$PML])
}

pairs(corrz[-1], lower.panel = panel.cor, 
      upper.panel = upper.panel)

```

